---
title: "SVC Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
source("L2 Dashboard.R")
```
All Segments
===================================== 

Column {data-width=350}
-----------------------------------------------------------------------

### SVCs per 100 Cases

```{r}
totalRatioPlot("All")
```

### 

```{r}
knitr::kable(totalRatio("All"), align = 'c')
```

```{r}
knitr::kable(avgRatio("All"), align = 'c')
```

Column {data-width=500}
-----------------------------------------------------------------------

### Top 10 SVCs Last Month

```{r}
topResLastMonth("All")
```
SVCs in 2021
```{r}
knitr::kable(resBreakdown("All"))

```

Enterprise
=====================================

Column {data-width=350}
-----------------------------------------------------------------------

### SVCs per 100 Cases
```{r}
totalRatioPlot("Enterprise")

```

###
```{r}
knitr::kable(totalRatio("Enterprise"), align = 'c')
```

```{r}
knitr::kable(avgRatio("Enterprise"), align = 'c')
```

Column {data-width=500}
-----------------------------------------------------------------------
### Top 10 SVCs Last Month
```{r}
topResLastMonth("Enterprise")

```
SVCs in 2021
```{r}
knitr::kable(resBreakdown("Enterprise"))
```


Mid Market 
===================================== 
Column {data-width=350}
-----------------------------------------------------------------------

### SVCs per 100 Cases
```{r}
totalRatioPlot("Mid Market")

```

###
```{r}
knitr::kable(totalRatio("Mid Market"), align = 'c')
```

```{r}
knitr::kable(avgRatio("Mid Market"), align = 'c')
```

Column {data-width=500}
-----------------------------------------------------------------------
### Top 10 SVCs Last Month
```{r}
topResLastMonth("Mid Market")

```
SVCs in 2021
```{r}
knitr::kable(resBreakdown("Mid Market"))
```


Small Business
===================================== 
Column {data-width=350}
-----------------------------------------------------------------------

### SVCs per 100 Cases
```{r}
totalRatioPlot("Small")

```

###
```{r}
knitr::kable(totalRatio("Small"), align = 'c')
```

```{r}
knitr::kable(avgRatio("Small"), align = 'c')
```

Column {data-width=500}
-----------------------------------------------------------------------
### Top 10 SVCs Last Month
```{r}
topResLastMonth("Small")

```
SVCs in 2021
```{r}
knitr::kable(resBreakdown("Small"))
```


NetX
===================================== 
Column {data-width=350}
-----------------------------------------------------------------------

### SVCs per 100 Cases
```{r}
totalRatioPlot("NetX")

```

###
```{r}
knitr::kable(totalRatio("NetX"), align = 'c')
```

```{r}
knitr::kable(avgRatio("NetX"), align = 'c')
```

Column {data-width=500}
-----------------------------------------------------------------------
### Top 10 SVCs Last Month
```{r}
topResLastMonth("NetX")

```
SVCs in 2021
```{r}
knitr::kable(resBreakdown("NetX"))
```

Five Star
===================================== 
Column {data-width=350}
-----------------------------------------------------------------------

### SVCs per 100 Cases
```{r}
totalRatioPlot("Five Star")

```

###
```{r}
knitr::kable(totalRatio("Five Star"), align = 'c')
```

```{r}
knitr::kable(avgRatio("Five Star"), align = 'c')
```

Column {data-width=500}
-----------------------------------------------------------------------
### Top 10 SVCs Last Month
```{r}
topResLastMonth("Five Star")

```
SVCs in 2021
```{r}
knitr::kable(resBreakdown("Five Star"))
```

Not Coded
===================================== 
Column {data-width=350}
-----------------------------------------------------------------------
### Not Coded Resolution or Subresolution
```{r}
knitr::kable(na_per)
```

Column {data-width=350}
-----------------------------------------------------------------------
### Recently Not Coded
```{r}
knitr::kable(recent_na)
```
